---
title: "High Level Overview of What this Package Contains"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{High Level Overview of What this Package Contains}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753nguy06282025)
```

# Example Usage of Functions

```{r}
set.seed(123)
values <- sample(1:100, 15, replace = TRUE)
```

## Example 1
```{r}
Lab1_quickBox(values)
```
## Example 2
```{r}
Lab2_zScore(values)
```
## Example 3
```{r}
dat <- data.frame(fire)
Lab4_fitVsResPlot(dat, dat$DISTANCE, dat$DAMAGE)
```
## Example 4
```{r}
myboot2(x=values)
```

# Function Details

## Lab1_quickBox

A boxplot function that accepts values.

## Lab2_zScore

Finds z-scores for values.

## Lab3_quickPlot

Returns a line plot (with steelblue!)

## Lab4_fitVsResPlot

Creates residual vs fitted plot with a linear model.

## Lab5_mybin

Creates a barplot displaying relative frequency.

## Lab6_myncurve

Creates a density plot using dnorm given a mean and standard deviation

## Lab8_mycltb

Density plot with central limit theorem.

## myboot2

Creates a bootstrap density plot with confidence intervals.

## mymaxlik

Findings maximum likelihood.

## project1_ntickets

Calculates the number of tickets to be sold when the number of seats in the flight.

# Data Details
## Fire
A data set collected containing fire DAMAGE and DISTANCE from fire stations.
